Exploring and Validating the Motives Behind API Evolution: A Case Study

### 2015-03-20 rmtw/a6/latex8.tex
sadads

Following the analysis of the archival data, the results of the interviews were analysed. The interviews were analysed using the same approach taken for the archival data. The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated.

@@

Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.

@@

%Internal Validity
\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed. By performing a individual inspection of  the API source code, documentation and individual results analysis, \textit{internal validity} is significantly reduced. Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.

>>>>

Following the analysis of the archival data, the results of the interviews were analysed. The interviews were analysed using the same approach taken for the archival data. The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated. This was done to triangulate the our findings, to help reduce internal validity.

@@

@@

%Internal Validity
\textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed. By performing a individual inspection of  the API source code, documentation and individual results analysis, \textit{internal validity} is significantly reduced. Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.
